\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-03 paper.tex
4. Cleared out the WOT. Improved the ending.

\subsubsection{Interests of the Player}
By purchasing a game like World of Warcraft, players are committing themselves to pay Blizzard Entertainment every month. \cite{WoWSubscription} Some players are reaping benefits that they would not be able to get otherwise, such as an increase in social interactions. \cite{IsThereEvidenceOfInternetAddiction} Users who play the game rarely navigate the world alone, instead they form groups with other players, join guilds, and tackle quests and dungeons that require teamwork and talking to others.
One particular study found that MMORPG users play for a mixture of ten reasons: advancement, mechanics, competition, socializing, relationship, teamwork, discovery, role-playing, customization, and escapism. These ten reasons break down into three components: achievement, social, and immersion. \cite{PlayerMotivations} The achievement component encompasses achievement, ``the desire to gain power, progress rapidly, and accumulate in-game symbols of status or wealth,'' mechanics, ``having an interest in analyzing the underlying rules and system in order to optimize character performance,'' and competition, ``the desire to challenge and compete with others.'' The social component deals with socializing, ``having an interest in helping and chatting with other players,'' relationship, ``the desire to form long-term meaningful relationships with others,'' and teamwork, ``deriving satisfaction from being part of a group effort.'' Lastly, the immersion component is discovery, ``finding and knowing things that most other players don't know about,'' role-playing, ``creating a persona with a background story and interacting with other players to create improvised story,'' customization, ``having an interest in customizing the appearance of their character,'' and escapism, ``using the online environment to avoid thinking about real life problems.'' \cite{PlayerMotivations} (All information following in this section is from the same study. \cite{PlayerMotivations}) MMORPGs offer a sense of achievement through completing quests, challenging others, and optimizing character performance. MMORPGs offer the chance to socialize with people you've never met, join groups to accomplish tasks, and form relationships with people through guilds and group events. MMORPGs also offer a sense of immersion through their expansive worlds that can be explored, the opportunity to role-play with others, the ability to customize your characters in a nearly infinite set of ways, and the chance to step into a different world where your real-world problems fade away. The interests of the player boil down to achievements, social interaction, and immersion in a world outside their own.

>>>>

\subsubsection{Interests of the Player}
By purchasing a game like World of Warcraft, players are committing themselves to pay Blizzard Entertainment every month. \cite{WoWSubscription} Some players are reaping benefits that they would not be able to get otherwise, such as an increase in social interactions. \cite{IsThereEvidenceOfInternetAddiction} Users who play the game rarely navigate the world alone, instead they form groups with other players, join guilds, and tackle quests and dungeons that require teamwork and talking to others.
One particular study found that MMORPG users play for a mixture of ten reasons: advancement, mechanics, competition, socializing, relationship, teamwork, discovery, role-playing, customization, and escapism. These ten reasons break down into three components: achievement, social, and immersion. \cite{PlayerMotivations} The interests of the player boil down to a sense of achievement, having social interactions, and immersion in a world outside their own.
